---
title   : "Apollo Training"
subtitle: "Train-the-trainer"
author  : "F.J. Padt"
date    : "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    toc: yes
  pdf_document:
    highlight: tango
    toc: yes
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

[R4DS](http://r4ds.had.co.nz/introduction.html)

# Objective


```{r setup}
# # Cleanse memory
# rm(list = ls())
# gc()

# parameters Settings
pXLSX    <- "" 
pWSHT    <- TRUE
newfiles <- TRUE
BIDOCsrc <- normalizePath("~/../../GrandVision/SAP BI documentation - Documents/bi-doc/src/")

# KnitR SetUp location
KS   <- file.path("~", "RW",
                  "QAR", "00_RProj", "00_Global", "KnitR_SetUp.R")

# Load functions
invisible(source(KS))

# FTP - Connection to GV FileServer
# Constants
# folder  <- "/bi/ib/md"          
# lfolder <- file.path("..", folder)  # local folder
# fsurl   <- paste0(
#   "ftp://fs.grandvision.com/pythia/", folder)
# userpwd <- paste("ftpbp1", params$password, sep = ":")

```

# Data Import

```{r Import}
AGR_USERS <-  
  fRead_and_Union(
    pSIDCLNT = c("BP1300"),
    pTable   = "AGR_USERS") %>%
  .[, TO_DAT := make_date(substr(TO_DAT, 1, 4), substr(TO_DAT, 5, 6), substr(TO_DAT, 7, 8)) ] %>%
  .[TO_DAT >= today()] %>%
  .[, .(SYSTID, CLIENT, AGR_NAME, UNAME, TO_DAT )] %>%
  .[substr(AGR_NAME, 1,8) == 'ZC:GVBI_']

AGR_USERS_BCK <- 
  copy(AGR_USERS)

# USR02 <- 
#   fRead_and_Union(
#     # pEnv   = "B",
#     pSIDCLNT = c("BD1100","BU1300","BA1300","BP1300"),    
#     pTable = "USR02",
#     pFields = list("BNAME", "TRDAT", "LTIME")  )
# 
# fOpen_in_Excel(
#   USR02, 
#   pFN = "USR02.csv")
```

# no authorisation for se37 might change the user to RFC User
# USR02 <-
#   fRead_and_Union(
#     pSIDCLNT = "MP1200",
#     pTable   = "USR02",
#     pOptions = list())

dtKEY <- 
  fread("APOLLO_KEY_USERS.csv")

dtEVAL <- 
  read_excel(
    path    = "Evaluation_form_results.xlsx",
    sheet   = "RESULTS",
    trim_ws = TRUE) %>%
  data.table()
```

# Tidy

```{r Tidy}

dtLabels <- 
  data.table(
    SUB = c(
      "BEFORE"   , "AFTER"   , "OBJ1"       , "OBJ2", "OBJ3",
      "TEACHING" , "HANDOUTS", "DISCUSSIONS",
      "EXERCISES", "SUPPORT" , "QUIZ"       , "KNOWLEDGE",
      "INTEREEST", "RELATING", "NEEDS"      , "Q_A",
      "ADMIN_ENROLL", "ROOM", "LOCATION", "RECOMMEND"),
    Subject = c(
      "Before"   , "After"   , 
      "What is BI?", "Getting Help", "Tool training",
      "Teaching" , "Handouts", "Discussions",
      "Exercises", "Support" , "Quiz", "Knowledge",
      "Motivating", "Relating", "Needs", "Questions & Answers",
      "Enrollment", "Room", "Location", "Recommend?")) 

dtRATING <- 
  dtEVAL[TOPIC != "ROLE" & SUB != "COMMENT" & !is.na(RATING)] %>%
  .[, RATING := as.integer(RATING)]  %>%
  dtLabels[., on = .(SUB)]

caption <- "(based on 12 forms)"
```


# Transform

```{r Transform}

dtAPOLLO <- 
  fGetSAPUsers(pType = "B")           %>%
  .[substr(CLASS, 1, 2) == "DE" & 
      USTYP             == "A"  &
      USR_GLTGB          > today()]   %>%
  dtKEY[., on = .(BNAME)]             %>%
  AGR_USERS[., on = .(SYSTID, 
                      CLIENT, 
                      UNAME = BNAME)]
  
```

# Visualize

```{r Visualize}
vrecommend <- c("Yes", "No", "other") 
cols <- c("green", "red", "gray")
names(cols) <- vrecommend

dtAVG <- 
  dtRATING[!is.na(RATING), .(average = mean(RATING)), 
           by = .(TOPIC, Subject)] %>%
  .[, average := round(average, 1)]

dtFINAL <- 
  dtRATING[TOPIC == "FINAL"]         %>%
  .[, Recommend := as.factor(RATING)]  

levels(dtFINAL$Recommend) <- vrecommend

ggFINAL <- 
  ggplot(
    data    = dtFINAL,
    mapping = aes(x = Recommend))  +
  geom_bar(aes(fill = Recommend)) +
  scale_fill_manual(
    values = cols,
    labels = vrecommend) +
  labs(caption = caption)               

ggFINAL

# dtTOPIC <- 
  # dtRATING[TOPIC != "FINAL" & TOPIC == "SKILLS"]  %>%
  # dcast.data.table(
  #   data          = .,
  #   formula       =  FORM + TOPIC + QUESTION ~SUB,
  #   fun.aggregate = sum,
  #   value.var     = "RATING")
  # 

ggSKILLS <- 
  ggplot(
    data = dtRATING[TOPIC == "SKILLS"],
    mapping = aes(x = SUB, y = RATING)) + 
  geom_violin(aes(colour = SUB, fill = SUB), width = 2,
              adjust = 0.25, trim = FALSE)            +
  geom_jitter(colour = "red", 
              height = 0, width = 0.2 )  +
  coord_flip()                          +
  labs(title = "Skills")                +
  labs(y     = "Rating")                +
  labs(x     = "Training")              +
  labs(caption = caption)               +
  scale_y_continuous(breaks = 1:5 , limits = c(1, 5)) +
  scale_colour_discrete(guide = FALSE)    +
  scale_fill_manual(
    values = c(BEFORE = "red", AFTER = "green" ),
    labels = c("BEFORE","AFTER"), 
    guide = FALSE) 

ggSKILLS

ggTRAINER <- 
  ggplot(
    data = dtRATING[TOPIC == "TRAINER" & !is.na(RATING)],
    mapping = aes(x = Subject, y = RATING)) + 
  geom_violin(aes(colour = SUB, fill = SUB), width = 2,
              adjust = 0.25, trim = FALSE)            +
  geom_jitter(colour = "red", 
              height = 0, width = 0.2 )  +
  coord_flip()                          +
  labs(title = "Trainer")               +
  labs(y     = "Rating")                +
  labs(x     = "Training")              +
  labs(caption = caption)               +
  scale_y_continuous(breaks = 1:5 , limits = c(1, 5)) +
  scale_colour_discrete(guide = FALSE)    +
  scale_fill_discrete(guide = FALSE) 

ggTRAINER
# ggsave(ggTRAINER, filename = "trainer.png", device = "png")
  

ggRELEVANCE <- 
  ggplot(
    data = dtRATING[TOPIC == "RELEVANCE" & !is.na(RATING)],
    mapping = aes(x = Subject, y = RATING)) + 
  geom_violin(aes(colour = SUB, fill = SUB), width = 2,
              adjust = 0.05, trim = FALSE)            +
  geom_jitter(colour = "red", 
              height = 0, width = 0.2 )  +
  coord_flip()                          +
  labs(title = "RELEVANCE")               +
  labs(y     = "Rating")                +
  labs(x     = "Training")              +
  labs(caption = caption)               +
  scale_y_continuous(breaks = 1:5 , limits = c(1, 5)) +
  scale_colour_discrete(guide = FALSE)    +
  scale_fill_discrete(guide = FALSE) 

ggRELEVANCE

ggMETHODS <- 
  ggplot(
    data = dtRATING[TOPIC == "METHODS" & !is.na(RATING)],
    mapping = aes(x = Subject, y = RATING)) + 
  geom_violin(aes(colour = SUB, fill = SUB), width = 2,
              adjust = 0.5, trim = FALSE)            +
  geom_jitter(colour = "red", 
              height = 0, width = 0.2 )  +
  coord_flip()                          +
  labs(title = "METHODS")               +
  labs(y     = "Rating")                +
  labs(x     = "Training")              +
  labs(caption = caption)               +
  scale_y_continuous(breaks = 1:5 , limits = c(1, 5)) +
  scale_colour_discrete(guide = FALSE)    +
  scale_fill_discrete(guide = FALSE) 

ggMETHODS

ggADMIN <- 
  ggplot(
    data = dtRATING[TOPIC == "ADMIN" & !is.na(RATING)],
    mapping = aes(x = Subject, y = RATING)) + 
  geom_violin(aes(colour = SUB, fill = SUB), width = 2,
              adjust = 0.25, trim = FALSE)            +
  geom_jitter(colour = "red", 
              height = 0, width = 0.2 )  +
  coord_flip()                          +
  labs(title = "ADMIN")               +
  labs(y     = "Rating")                +
  labs(x     = "Training")              +
  labs(caption = caption)               +
  scale_y_continuous(breaks = 1:5 , limits = c(1, 5)) +
  scale_colour_discrete(guide = FALSE)    +
  scale_fill_discrete(guide = FALSE) 

ggADMIN

fOpen_in_Excel(
  dtAPOLLO[SYSTID == "BP1" & TRAIN == "Y"], 
  pFN = "APOLLO_USER.csv")

fOpen_in_Excel(
  dtKEY, 
  pFN = "APOLLO_TRN.csv")
```

# Model

```{r Model}

```

# Communicate

```{r Communicate}

```


