---
title   : "R1 to R2"
subtitle: "Query Documention"
author  : "F.J. Padt"
date    : "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    toc: yes
  pdf_document:
    highlight: tango
    toc: yes
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

[R4DS](http://r4ds.had.co.nz/introduction.html)

# Objective


```{r setup}
# # Cleanse memory
# rm(list = ls())
# gc()

# parameters Settings
pXLSX    <- "" 
pWSHT    <- TRUE
newfiles <- TRUE
BIDOCsrc <- normalizePath("~/../../GrandVision/SAP BI documentation - Documents/bi-doc/src/")

# KnitR SetUp location
KS   <- file.path("~", "RW",
                  "QAR", "00_RProj", "00_Global", "KnitR_SetUp.R")

# Load functions
invisible(source(KS))

# FTP - Connection to GV FileServer
# Constants
# folder  <- "/bi/ib/md"          
# lfolder <- file.path("..", folder)  # local folder
# fsurl   <- paste0(
#   "ftp://fs.grandvision.com/pythia/", folder)
# userpwd <- paste("ftpbp1", params$password, sep = ":")

```

# Data Import

```{r Import}
MIG  <- file.path("C:", "Users", "fpadt", "GrandVision", "iSynergy - 90 BI",
                  "70. Migration") 
pINFO    <- file.path(MIG, "INFO_MD.xlsx") 

dtRSRREPDIR <-
  fRead_and_Union(
    pType    = "B",
    pTable   = "RSRREPDIR",
    pOptions = list("OBJVERS = 'A'"),
    pFields  = list("COMPUID" , "INFOCUBE", "COMPTYPE", "COMPID" , "RFCSUPPORT", "OBJSTAT",
                    "READMODE", "REPTIME" , "LASTUSER", "MODTIME", "GEN1TIME"  , "IS_PLANQUERY"))

dtRSZCOMPDIR <-
  fRead_and_Union(
    pType    = "B",
    pTable   = "RSZCOMPDIR",
    pOptions = list("OBJVERS = 'A'"),
    pFields = list("COMPUID", "COMPID"  , "OWNER", 
                   "ACTIVFL", "TIMESTMP", "LASTUSED", "CREATED"))

dtTADIR <-
  fRead_and_Union(
    pSIDCLNT = "BP1300",
    pTable   = "TADIR",
    pOptions = list("SRCSYSTEM like 'B%'"))

dtUSR02 <-
  fRead_and_Union(
    pSIDCLNT = "BP1300",
    pTable   = "USR02",
    pFields  = list("BNAME", "TRDAT", "CLASS", "USTYP", "UFLAG", "GLTGB"))

dtUSR21 <-
  fRead_and_Union(
    pSIDCLNT = "BP1300",
    pTable   = "USR21",
    pOptions = list())

dtADR6 <-
  fRead_and_Union(
    pSIDCLNT = "BP1300",
    pTable   = "ADR6",
    pOptions = list())

dtAUTH <-
  fRead_and_Union(
    pSIDCLNT = "BP1300",
    pTable   = "/BIC/AG1AAPD222",
    pFields = list("/BIC/G1AAGRP", "/BIC/G1AAOBJ", "/BIC/G1AASIGN", "/BIC/G1AAOPT", "/BIC/G1AAVAL_L",
                   "RECORDMODE", "/BIC/G1AAVAL_H", "/BIC/G1COUNT")) %T>%
  setnames(gsub(pattern = "/BIC/", replacement = "", x = names(.)))

# Read data from Local Excel File, note stats need to be refreshed
dtCOMM       <- as.data.table(read_excel(path = pINFO, sheet = "C.OMMENT"))
dtDSO        <- as.data.table(read_excel(path = pINFO, sheet = "D.SO"))    
dtJIRA       <- as.data.table(read_excel(path = pINFO, sheet = "J.IRA"))  
dtOBJR       <- as.data.table(read_excel(path = pINFO, sheet = "O.BJR"))
dtRTST       <- as.data.table(read_excel(path = pINFO, sheet = "R.TST"))  
dtSTAT       <- as.data.table(read_excel(path = pINFO, sheet = "S.TAT"))
dtTEAM       <- as.data.table(read_excel(path = pINFO, sheet = "T.EAM"))
dtUSER       <- as.data.table(read_excel(path = pINFO, sheet = "U.SER"))
dtWEBI       <- as.data.table(read_excel(path = pINFO, sheet = "W.EBI"))

# rename columns coming from teh BW statistics
setnames(dtSTAT, c("S.CDAY", "S.COMPID", "S.QDESCR", "S.USER", "S.QEXEC"))


```

# Tidy

```{r Tidy}

```

Q0. remove "$"
Q1. query on $TMP per first character G/L/Z
Q2. query Last USed, Last User, Top User, IDLE time, #Users, #OPCO's last Month, AGE
U1. Which OPCO, DEP, User+Mail
Dx. GBPO/LBPO, Process, Author, Link to DoC, TD/FD
Bx. Query in whcih BO reports/folders
Reports per DSO R1 -> R2
How many R1/R2 reports
Q3. Mapping R1 -> R2
4. RT Quereis 
9 .z-> L/G

1. at the end the stats need to be distributed
2. calculate the life and idle time based on creation data and last used and current day

### regression test
[RT GVBNL](http://report.grandvision.global/test/r2fr/rt1/bubbles_bi_gvblx.html)

# Transform

```{r Transform}
# remove fields
# dtRSRREPDIR <- 
#   dtRSRREPDIR[, .(SYSTID    , COMPUID , INFOCUBE, COMPTYPE, COMPID, 
#                   RFCSUPPORT, OBJSTAT , READMODE, LASTUSER, MODTIME, 
#                   REPTIME   , GEN1TIME, IS_PLANQUERY)]

# dtRSZCOMPDIR <-
#   dtRSZCOMPDIR[, .(SYSTID , COMPUID , COMPID  , OWNER, 
#                    ACTIVFL, TIMESTMP, LASTUSED, CREATED)] 

setnames(dtRSRREPDIR,  paste("B", names(dtRSRREPDIR),  sep = "."))
setnames(dtRSZCOMPDIR, paste("B", names(dtRSZCOMPDIR), sep = "."))
setnames(dtTADIR,      paste("B", names(dtTADIR),      sep = "."))
setnames(dtUSR02,      paste("B", names(dtUSR02),      sep = "."))
setnames(dtUSR21,      paste("B", names(dtUSR21),      sep = "."))
setnames(dtADR6,       paste("B", names(dtADR6),       sep = "."))
setnames(dtAUTH,       paste("B", names(dtAUTH),       sep = "."))

dtINFOPROV <- 
  dtOBJR[dtTADIR[, .(B.SYSTID   , B.OBJECT, B.OBJ_NAME, 
                     B.SRCSYSTEM, B.AUTHOR, B.DEVCLASS )], 
         on = .(O.OBJECT_IP = B.OBJECT), 
         nomatch = 0]                    

dtINFOPROV <- 
  unique(dtINFOPROV[, .(B.SYSTID, B.OBJ_NAME, B.SRCSYSTEM, 
                        B.AUTHOR, B.DEVCLASS, O.REL_IP )])

dtSTAT[, S.CDAY := format(ymd(S.CDAY), "%d-%m-%Y")]

# Split the Tech Query name in parts and set checks
dtDIR <- 
  dtRSRREPDIR[!B.COMPID == "" & B.COMPTYPE == "REP"]       %>%
  .[, paste0("B.QPART", 1:6) := tstrsplit(B.COMPID, "_", 
                                        fixed = TRUE, 
                                        fill  = "")]       %>%
  .[, `:=`(
    B.IN_BP1 = B.COMPID %in% dtRSRREPDIR[B.SYSTID == "BP1", 
                                         B.COMPID],
    B.QNS     = substr(B.QPART1, 1, 1),  # Name Space
    B.QTG     = substr(B.QPART1, 2, 3),  # Target Group
    B.QIP     = B.QPART2       ,         # InfoProvider
    B.QAA     = substr(B.QPART2, 3, 4),  # Application Area
    B.QIP_TP  = substr(B.QPART2, 5, 6),  # InfoProvider Type
    B.QL1     = nchar(B.QPART1),         # Number of Char part 1
    B.QL2     = nchar(B.QPART2),         # Number of Char part 2
    B.QL3     = nchar(B.QPART3),         # Number of Char part 3
    B.QLPC    = nchar(B.QPART1) == 3 & 
      nchar(B.QPART3) %in% c(3, 4))]                       %>%
  .[, `:=`(
    B.IAA     = substr(B.COMPID, 7, 8),
    B.IPT     = substr(B.COMPID, 9, 10),
    B.INS     = substr(B.QPART1, 1, 1),
    B.ITG     = substr(B.QPART1, 1, 2), 
    B.CHK_IP  = B.INFOCUBE == B.QIP,     # Check if name of query is correct
    B.CHK_AA  = B.QAA    == substr(B.COMPID, 7, 8),
    B.CHK_TP  = B.QIP_TP == substr(B.COMPID, 9, 10))]      %>%
  dtRSZCOMPDIR[.,
               on = .(B.SYSTID, B.COMPUID, B.COMPID),
               nomatch = 0]                                %>%
  dtTADIR[B.OBJECT == "ELEM", 
          .(B.SYSTID, B.OBJECT  , B.OBJ_NAME  , B.SRCSYSTEM,
            B.AUTHOR, B.DEVCLASS, B.CREATED_ON)
          ][.,
            on = .(B.SYSTID, B.OBJ_NAME == B.COMPUID),
            nomatch = NA]                                  %T>%
  setnames(c("B.OBJECT"       , "B.OBJ_NAME"     , 
             "B.SRCSYSTEM"    , "B.AUTHOR"       , 
             "B.DEVCLASS"     , "B.CREATED_ON")  ,
           c("B.OBJECT_REP"   , "B.OBJ_NAME_REP" , 
             "B.SRCSYSTEM_REP", "B.AUTHOR_REP"   , 
             "B.DEVCLASS_REP" , "B.CREATED_ON_REP"))       %>%
  .[, B.INFOPROV := sub(pattern   = "@3", 
                      replacement = "", 
                      x           = B.INFOCUBE)]           %>%
  dtINFOPROV[.,
             on = .(B.SYSTID, B.OBJ_NAME == B.INFOPROV),
             nomatch = NA]                                 %T>%
  setnames(c("B.OBJ_NAME"     ,
             "B.SRCSYSTEM"    , "B.AUTHOR"       ,
             "B.DEVCLASS")    ,
           c("B.OBJ_NAME_IP"  ,
             "B.SRCSYSTEM_IP" , "B.AUTHOR_IP"    ,
             "B.DEVCLASS_IP"))                             %>%
  .[, B.CNT := .N, by = .(B.COMPID)]                          

```

```{r addAuths}
dtDIR <- 
  dtAUTH[B.G1AAOBJ == "QUERY" & B.SYSTID == "BP1",
           .(B.G1AAGRP, B.G1AAVAL_L)][dtDIR, 
    on = .(B.G1AAVAL_L == B.COMPID), nomatch = NA ]         %>%
  .[, B.COMPID := B.G1AAVAL_L ]
```


```{r COE_COMMENTS}

dtCOE <- 
  dcast.data.table(
    dtDIR[, .(B.COMPID, B.SYSTID)], 
    fun.aggregate = length,
    value.var     = "B.SYSTID",
    formula       = B.COMPID ~ B.SYSTID)                   %>%
  #  .[ BD1 == 1 & (BA1 + BP1 + BTP + BU1) == 0, 
  #     COE := "CHECK if New/Old Development"]             %>%
  .[, COE := ""]                                           %>%  
  .[ BD1 == 1 & (BA1 + BP1) == 0, 
     COE := paste(COE, 
                  "CHECK if New/Old Development", 
                  sep = " \n ")]                           %>%
  .[ (BD1 + BA1) == 2 & (BP1) == 0, 
     COE := paste(COE, 
                  "CHECK if new R2 Development", 
                  sep = " \n ")]                           %>%
  #  .[ (BD1 + BA1 + BTP + BP1) == 4 & (BU1) == 0, 
  #     COE := "TRANSPORT TO BU1"]                         %>%
  #  .[ (BTP) == 0 & (BU1) == 1, 
  #     COE := "TRANSPORT TO BTP"]                         %>%
  #  .[ (BD1 + BA1 + BTP + BP1 + BU1) == 5, 
  #     COE := "CHECK to be Authorized"]                   %>%
  .[ BD1 == 0, 
     COE := paste(COE, 
                  "DELETE AS NOT in BD1", 
                  sep = " \n ")]                           %>%     
  .[ is.na(COE), 
     COE := paste(COE, 
                  "CHECK SPECIAL CASE?", 
                  sep = " \n ")]                           %>%     
  .[ substr(B.COMPID, 1, 1) == "Z", 
     COE := paste(COE, 
                  "DELETE or REBUILD as G/L", 
                  sep = " \n ")]                           %>%     
  .[dtDIR, on = .(B.COMPID), nomatch = NA]                 %>%
  .[ (BD1 + BA1 + BP1) == 3 & is.na(B.G1AAGRP), 
     COE := paste(COE, 
                  "CHECK to be Authorized", 
                  sep = " \n ")]                           %>%  
  .[ (BD1 + BA1 + BP1) == 3 & !is.na(B.G1AAGRP), 
     COE := paste(COE, 
                  "CHECK if Documented", 
                  sep = " \n ")]                           %>%
  .[B.DEVCLASS_REP == "$TMP" & B.INS != "Z",
    COE := paste(COE, 
                 "DELETE QUERY", 
                 sep = " \n ")]                            %>%
  .[B.DEVCLASS_REP == "$TMP" & B.INS != "Z" & 
      !is.na(B.G1AAVAL_L),
    COE := paste(COE, 
                 "REMOVE AUTHORIZATION", 
                 sep = " \n ")]  


```


```{r GetStats}
# Set Flag User Status

dtUSR <- 
  dtUSR21[dtADR6, on = .(B.SYSTID, B.MANDT = B.CLIENT, 
                         B.PERSNUMBER, B.ADDRNUMBER),
          nomatch = 0]                                     %>%
  .[, .(B.SYSTID, B.CLIENT, B.BNAME, B.SMTP_ADDR)]         %>%
  .[dtUSR02, on = .(B.SYSTID, B.CLIENT, B.BNAME), 
    nomatch = NA]   

dtUSR[, B.USTATE := ifelse(
  B.GLTGB >= format( Sys.Date(), format = "%Y%m%d"),
  "VALID", "INVALID") ]

dtUSR[, B.USTATE := ifelse(
  B.USTATE == "VALID" & B.UFLAG == "0",
  "VALID", "LOCKED") ]

dtUSR <- 
  dtUSR[, .(B.BNAME, B.SMTP_ADDR, 
            B.CLASS, B.USTYP, B.USTATE)]                   %>%
  .[dtUSER, on = .(B.CLASS = U.CLASS)]                     %>%
  .[dtSTAT, on = .(B.BNAME = S.USER)]                      %>%
  .[dtCOE[B.SYSTID == "BP1"], 
    on = .(S.COMPID = B.COMPID)]                           %>%
  .[, `:=`(U.CLASS  = B.CLASS,
           S.USER   = B.BNAME,
           B.COMPID = S.COMPID)]

```

```{r addInfo}
dtINFO <-
  dtUSR                                                    %>%
  dtTEAM[., on = .(T.OWNER  == B.OWNER) , nomatch = NA]    %>%
  dtWEBI[., on = .(W.COMPID == S.COMPID), nomatch = NA, 
         allow.cartesian = TRUE]                           %>%
  dtCOMM[., on = .(C.COMPID == W.COMPID), nomatch = NA]    %>%
  .[, `:=`(B.OWNER  = T.OWNER,
           S.COMPID = C.COMPID,
           W.COMPID = C.COMPID)]                
  
```

```{r CleanseMem}
rm(dtADR6     , dtUSR21     , dtUSR02   , dtUSER,
   dtTEAM     , dtTADIR     , dtSTAT    , dtPATH, 
   dtDIR      , dtCOE       , dtUSR,
   dtCOMM      , dtWEBI      , dtOBJR, 
   dtRSRREPDIR, dtRSZCOMPDIR, dtINFOPROV)
```

```{r prePare}
setcolorder(dtINFO, sort(names(dtINFO)))

dtINFO <- 
  dtINFO[B.OWNER != "SAP"] %>%
  .[, `:=`(
    B.ACTIVFL = NULL)]



```

# Model

```{r model_find_$tmp_neq_Z}
fOpen_in_Excel(pDT = dtINFO, pFN = "neq_z_eq_tmp.csv")
```


# Visualize

```{r Visualize}

```


# Communicate

```{r Communicate}

pFFN <- normalizePath(file.path("~", "RW", "QAR", "30_Analysis", "FileName.csv"))

write.table(
  pOBJ,
  file = pFFN, 
  sep = ";", row.names = FALSE, col.names = TRUE)
shell.exec(pFFN)
```


