---
title   : "Quality Assurance Report"
subtitle: "R1 -> R2 Migration"
author  : "F.J. Padt"
date    : "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: no
    toc_depth: 4
classoption: landscape
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  eval    = TRUE,
  message = FALSE,
  warning = FALSE,
  image   = TRUE,
  results = "hide")

# Cleanse memory
rm(list = ls())
gc()

# folder locations
RW   <- file.path("C:", "Users", "fpadt", "OneDrive - GrandVision", "RW")
PRJ  <- file.path(RW  , "QAR")
MOD  <- file.path(PRJ , "00_RProj")
DAT  <- file.path(PRJ , "11_PrepData")
RES  <- file.path(PRJ , "60_Results")
FIG  <- file.path(PRJ , "70_Figures")
MIG  <- file.path("C:", "Users", "fpadt", "GrandVision", 
                  "iSynergy - 70. Migration") 

#source('../pythia/SharedFunctions/GenericFunctions.R')
invisible(source(file.path(MOD, "00_Global", "iSynGeneral.R")))

# SAP systems to use
pECC_SYST <- "RP1"
pECC_CLNT <- "300"
pBI_SYST  <- "BP1"
pBI_CLNT  <- "300"
pLGCINDC  <- "C"

# Data Settings
pXLSX    <- "R12R2" 

pINFO    <- file.path(MIG, "INFO_MD.xlsx") 
# note VPN is needed for this doesn't work on internal network
# pINFO    <- "//grandvision.sharepoint.com/sites/NL1-Proj-iSynergy/05_CoE/90%20BI/INFOtst.xlsx"
pWSHT    <- TRUE
newfiles <- TRUE
SID.lng  <- c("BD1100", "BA1300", "BP1300") #, "BTP300", "BU1300")
SID.sht  <- substr(SID.lng, 1, 3)

dtPATH <- 
  data.table(
    DESCR = c("RW", "PRJ", "MOD", "FIG", "DAT", "RES"),
    PATH  = c( RW ,  PRJ ,  MOD ,  FIG ,  DAT ,  RES )
  )

# Open Excel for storing results
if (file.exists(paste0(RES, "/", pXLSX, ".xlsx")) == TRUE) {
  invisible(file.remove(paste0(RES, "/", pXLSX, ".xlsx")))
}

if (pWSHT == TRUE) {
  fWriteToSheet(
    dtPATH, 
    RES, pXLSX, "PATHS", pAppend = FALSE )}

gvLOGO_PATH <- file.path(FIG, "GV_LOGO.png") 
if (!file.exists(gvLOGO_PATH)) {
  download.file(
    url      = "http://www.grandvision.com/img/logoGV.png",
    destfile = gvLOGO_PATH,
    mode     = 'wb')
}
knitr::include_graphics(gvLOGO_PATH)

# First execute the analysis zsANALYSIS-R1R2_MIG
# Extecute mcrAnalysesExtract
# C:\Users\fpadt\SAPEXPORT


read_and_union <- function(pTableName){
  
  dtReturn <- 
    do.call(
      rbind,
      lapply(as.list(SID.lng), function(x) {
        fGetEXPTable(
          pTableName = pTableName,
          pSystID = substr(x, 1, 3),
          pClient = substr(x, 4, 6) )
      }))
  
  return(dtReturn)
}

# read data from MS Access extract
dtRSRREPDIR  <- read_and_union("RSRREPDIR")
dtRSZCOMPDIR <- read_and_union("RSZCOMPDIR")
dtTADIR      <- read_and_union("TADIR")
dtUSR02      <- fGetEXPTable(pTableName = "USR02", pSystID = "BP1", pClient = 300)
dtUSR21      <- fGetEXPTable(pTableName = "USR21", pSystID = "BP1", pClient = 300)  
dtADR6       <- fGetEXPTable(pTableName = "ADR6" , pSystID = "BP1", pClient = 300)  
dtAUTH       <- fGetEXPTable(pTableName = "#BIC#AG1AAPD0200"
                             , pSystID = "BP1", pClient = 300)  

# Read data from Local Excel File, note stats need to be refreshed
dtCOMM       <- as.data.table(read_excel(path = pINFO, sheet = "C.OMMENT"))
dtDSO        <- as.data.table(read_excel(path = pINFO, sheet = "D.SO"))    
dtJIRA       <- as.data.table(read_excel(path = pINFO, sheet = "J.IRA"))  
dtOBJR       <- as.data.table(read_excel(path = pINFO, sheet = "O.BJR"))
dtRTST       <- as.data.table(read_excel(path = pINFO, sheet = "R.TST"))  
dtSTAT       <- as.data.table(read_excel(path = pINFO, sheet = "S.TAT"))
dtTEAM       <- as.data.table(read_excel(path = pINFO, sheet = "T.EAM"))
dtUSER       <- as.data.table(read_excel(path = pINFO, sheet = "U.SER"))
dtWEBI       <- as.data.table(read_excel(path = pINFO, sheet = "W.EBI"))

# rename columns coming from teh BW statistics
setnames(dtSTAT, c("S.CDAY", "S.COMPID", "S.QDESCR", "S.USER", "S.QEXEC"))


```

Q0. remove "$"
Q1. query on $TMP per first character G/L/Z
Q2. query Last USed, Last User, Top User, IDLE time, #Users, #OPCO's last Month, AGE
U1. Which OPCO, DEP, User+Mail
Dx. GBPO/LBPO, Process, Author, Link to DoC, TD/FD
Bx. Query in whcih BO reports/folders
Reports per DSO R1 -> R2
How many R1/R2 reports
Q3. Mapping R1 -> R2
4. RT Quereis 
9 .z-> L/G

1. at the end the stats need to be distributed
2. calculate the life and idle time based on creation data and last used and current day

### regression test
[RT GVBNL](http://report.grandvision.global/test/r2fr/rt1/bubbles_bi_gvblx.html)


```{r Transform}
# remove fields
dtRSRREPDIR <- 
  dtRSRREPDIR[, .(SYSTID    , COMPUID , INFOCUBE, COMPTYPE, COMPID, 
                  RFCSUPPORT, OBJSTAT , READMODE, LASTUSER, MODTIME, 
                  REPTIME   , GEN1TIME, IS_PLANQUERY)]

dtRSZCOMPDIR <-
  dtRSZCOMPDIR[, .(SYSTID , COMPUID , COMPID  , OWNER, 
                   ACTIVFL, TIMESTMP, LASTUSED, CREATED)] 

setnames(dtRSRREPDIR,  paste("B", names(dtRSRREPDIR),  sep = "."))
setnames(dtRSZCOMPDIR, paste("B", names(dtRSZCOMPDIR), sep = "."))
setnames(dtTADIR,      paste("B", names(dtTADIR),      sep = "."))
setnames(dtUSR02,      paste("B", names(dtUSR02),      sep = "."))
setnames(dtUSR21,      paste("B", names(dtUSR21),      sep = "."))
setnames(dtADR6,       paste("B", names(dtADR6),       sep = "."))
setnames(dtAUTH,       paste("B", names(dtAUTH),       sep = "."))

dtINFOPROV <- 
  dtOBJR[dtTADIR[, .(B.SYSTID   , B.OBJECT, B.OBJ_NAME, 
                     B.SRCSYSTEM, B.AUTHOR, B.DEVCLASS )], 
         on = .(O.OBJECT_IP = B.OBJECT), 
         nomatch = 0]                    

dtINFOPROV <- 
  unique(dtINFOPROV[, .(B.SYSTID, B.OBJ_NAME, B.SRCSYSTEM, 
                        B.AUTHOR, B.DEVCLASS, O.REL_IP )])

dtSTAT[, S.CDAY := format(ymd(S.CDAY), "%d-%m-%Y")]

# Split the Tech Query name in parts and set checks
dtDIR <- 
  dtRSRREPDIR[!B.COMPID == "" & B.COMPTYPE == "REP"]       %>%
  .[, paste0("B.QPART", 1:6) := tstrsplit(B.COMPID, "_", 
                                        fixed = TRUE, 
                                        fill  = "")]       %>%
  .[, `:=`(
    B.IN_BP1 = B.COMPID %in% dtRSRREPDIR[B.SYSTID == "BP1", 
                                         B.COMPID],
    B.QNS     = substr(B.QPART1, 1, 1),  # Name Space
    B.QTG     = substr(B.QPART1, 2, 3),  # Target Group
    B.QIP     = B.QPART2       ,         # InfoProvider
    B.QAA     = substr(B.QPART2, 3, 4),  # Application Area
    B.QIP_TP  = substr(B.QPART2, 5, 6),  # InfoProvider Type
    B.QL1     = nchar(B.QPART1),         # Number of Char part 1
    B.QL2     = nchar(B.QPART2),         # Number of Char part 2
    B.QL3     = nchar(B.QPART3),         # Number of Char part 3
    B.QLPC    = nchar(B.QPART1) == 3 & 
      nchar(B.QPART3) %in% c(3, 4))]                       %>%
  .[, `:=`(
    B.IAA     = substr(B.COMPID, 7, 8),
    B.IPT     = substr(B.COMPID, 9, 10),
    B.INS     = substr(B.QPART1, 1, 1),
    B.ITG     = substr(B.QPART1, 1, 2), 
    B.CHK_IP  = B.INFOCUBE == B.QIP,
    B.CHK_AA  = B.QAA    == substr(B.COMPID, 7, 8),
    B.CHK_TP  = B.QIP_TP == substr(B.COMPID, 9, 10))]      %>%
  dtRSZCOMPDIR[.,
               on = .(B.SYSTID, B.COMPUID, B.COMPID),
               nomatch = 0]                                %>%
  dtTADIR[B.OBJECT == "ELEM", 
          .(B.SYSTID, B.OBJECT  , B.OBJ_NAME  , B.SRCSYSTEM,
            B.AUTHOR, B.DEVCLASS, B.CREATED_ON)
          ][.,
            on = .(B.SYSTID, B.OBJ_NAME == B.COMPUID),
            nomatch = NA]                                  %T>%
  setnames(c("B.OBJECT"       , "B.OBJ_NAME"     , 
             "B.SRCSYSTEM"    , "B.AUTHOR"       , 
             "B.DEVCLASS"     , "B.CREATED_ON")  ,
           c("B.OBJECT_REP"   , "B.OBJ_NAME_REP" , 
             "B.SRCSYSTEM_REP", "B.AUTHOR_REP"   , 
             "B.DEVCLASS_REP" , "B.CREATED_ON_REP"))       %>%
  .[, B.INFOPROV := sub(pattern   = "@3", 
                      replacement = "", 
                      x           = B.INFOCUBE)]           %>%
  dtINFOPROV[.,
             on = .(B.SYSTID, B.OBJ_NAME == B.INFOPROV),
             nomatch = NA]                                 %T>%
  setnames(c("B.OBJ_NAME"     ,
             "B.SRCSYSTEM"    , "B.AUTHOR"       ,
             "B.DEVCLASS")    ,
           c("B.OBJ_NAME_IP"  ,
             "B.SRCSYSTEM_IP" , "B.AUTHOR_IP"    ,
             "B.DEVCLASS_IP"))                             %>%
  .[, B.CNT := .N, by = .(B.COMPID)]                          

```

```{r addAuths}
dtDIR <- 
  dtAUTH[B.G1AAOBJ == "QUERY" & B.SYSTID == "BP1",
           .(B.G1AAGRP, B.G1AAVAL_L)][dtDIR, 
    on = .(B.G1AAVAL_L == B.COMPID), nomatch = NA ]         %>%
  .[, B.COMPID := B.G1AAVAL_L ]
```


```{r COE_COMMENTS}

dtCOE <- 
  dcast.data.table(
    dtDIR[, .(B.COMPID, B.SYSTID)], 
    fun.aggregate = length,
    value.var     = "B.SYSTID",
    formula       = B.COMPID ~ B.SYSTID)                   %>%
#  .[ BD1 == 1 & (BA1 + BP1 + BTP + BU1) == 0, 
#     COE := "CHECK if New/Old Development"]                %>%
  .[ BD1 == 1 & (BA1 + BP1) == 0, 
     COE := "CHECK if New/Old Development"]                %>%
  .[ (BD1 + BA1) == 2 & (BP1) == 0, 
     COE := "CHECK if new R2 Development"]                 %>%
#  .[ (BD1 + BA1 + BTP + BP1) == 4 & (BU1) == 0, 
#     COE := "TRANSPORT TO BU1"]                            %>%
#  .[ (BTP) == 0 & (BU1) == 1, 
#     COE := "TRANSPORT TO BTP"]                            %>%
#  .[ (BD1 + BA1 + BTP + BP1 + BU1) == 5, 
#     COE := "CHECK to be Authorized"]                      %>%
  .[ BD1 == 0, 
     COE := "DELETE AS NOT in BD1"]                        %>%
  .[ is.na(COE), 
     COE := "CHECK SPECIAL CASE?"]                         %>%
  .[ substr(B.COMPID, 1, 1) == "Z", 
     COE := "DELETE or REBUILD as G/L"]                    %>%
  .[dtDIR, on = .(B.COMPID), nomatch = NA]                 %>%
  .[ (BD1 + BA1 + BP1) == 3 & is.na(B.G1AAGRP), 
     COE := "CHECK to be Authorized"]                      %>% 
  .[ (BD1 + BA1 + BP1) == 3 & !is.na(B.G1AAGRP), 
     COE := "CHECK if Documented"]  
```


```{r GetStats}
# Set Flag User Status

dtUSR <- 
  dtUSR21[dtADR6, on = .(B.SYSTID, B.MANDT = B.CLIENT, 
                         B.PERSNUMBER, B.ADDRNUMBER),
          nomatch = 0]                                     %>%
  .[, .(B.SYSTID, B.MANDT, B.BNAME, B.SMTP_ADDR)]          %>%
  .[dtUSR02, on = .(B.SYSTID, B.MANDT, B.BNAME), 
    nomatch = NA]   

dtUSR[, B.USTATE := ifelse(
  B.GLTGB >= format( Sys.Date(), format = "%Y%m%d"),
  "VALID", "INVALID") ]

dtUSR[, B.USTATE := ifelse(
  B.USTATE == "VALID" & B.UFLAG == "0",
  "VALID", "LOCKED") ]

dtUSR <- 
  dtUSR[, .(B.BNAME, B.SMTP_ADDR, 
            B.CLASS, B.USTYP, B.USTATE)]                   %>%
  .[dtUSER, on = .(B.CLASS = U.CLASS)]                     %>%
  .[dtSTAT, on = .(B.BNAME = S.USER)]                      %>%
  .[dtCOE[B.SYSTID == "BP1"], 
    on = .(S.COMPID = B.COMPID)]                           %>%
  .[, `:=`(U.CLASS  = B.CLASS,
           S.USER   = B.BNAME,
           B.COMPID = S.COMPID)]

```

```{r addInfo}
dtINFO <-
  dtUSR                                                    %>%
  dtTEAM[., on = .(T.OWNER  == B.OWNER) , nomatch = NA]    %>%
  dtWEBI[., on = .(W.COMPID == S.COMPID), nomatch = NA, 
         allow.cartesian = TRUE]                           %>%
  dtCOMM[., on = .(C.COMPID == W.COMPID), nomatch = NA]    %>%
  .[, `:=`(B.OWNER  = T.OWNER,
           S.COMPID = C.COMPID,
           W.COMPID = C.COMPID)]                
  
```

```{r CleanseMem}
rm(dtADR6     , dtUSR21     , dtUSR02   , dtUSER,
   dtTEAM     , dtTADIR     , dtSTAT    , dtPATH, 
   dtDIR      , dtCOE       , dtUSR,
   dtCOMM      , dtWEBI      , dtOBJR, 
   dtRSRREPDIR, dtRSZCOMPDIR, dtINFOPROV)
```

```{r ExportTxt}
setcolorder(dtINFO, sort(names(dtINFO)))

write.table(
  dtINFO,
  file      = file.path(RES, "R12R2.csv"),
  sep       = ";",
  row.names = FALSE,
  col.names = TRUE,
  quote     = TRUE)
```

```{r ExportXLS, eval=FALSE, include=FALSE}
system.time(
  fWriteToSheet(dtINFO, 
                RES, pXLSX, "DATA", pAppend = FALSE )
)
```

