---
title   : "Quality Assurance Report"
subtitle: "Process Chains Schedule"
author  : "F.J. Padt"
date    : "`r format(Sys.time(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: no
    toc_depth: 4
classoption: landscape
---

```{r setup, echo=FALSE, results= "hide"}
knitr::opts_chunk$set(
  echo    = FALSE,
  eval    = TRUE,
  message = FALSE,
  warning = FALSE,
  image   = TRUE,
  results = "hide")

# Cleanse memory
rm(list = ls())
gc()

# folder locations
RW   <- file.path("C:", "Users", "fpadt", "OneDrive - GrandVision", "Documents", "RW")
PRJ  <- file.path(RW , "QAR")
MOD  <- file.path(PRJ, "00_RProj")
DAT  <- file.path(PRJ, "11_PrepData")
RES  <- file.path(PRJ, "60_Results")
FIG  <- file.path(PRJ, "70_Figures")

# Load functions
invisible(source(file.path(MOD, "00_Global", "iSynGeneral.R")))

# SAP systems to use
pECC_SYST <- "RP1"
pECC_CLNT <- "300"
pBI_SYST  <- "BP1"
pBI_CLNT  <- "300"
pLGCINDC  <- "C"

# Data Settings
pXLSX    <- "RSPC" 

# note VPN is needed for this doesn't work on internal network
# pINFO    <- "//grandvision.sharepoint.com/sites/NL1-Proj-iSynergy/05_CoE/90%20BI/INFOtst.xlsx"
pWSHT    <- TRUE
newfiles <- TRUE
# SID.lng  <- c("BA1300") #, "BTP300", "BU1300")
SID.lng  <- c("BD1100", "BU1300", "BA1300", "BP1300") #, "BTP300", "BU1300")
SID.sht  <- substr(SID.lng, 1, 3)

# set_theme()

dtPATH <- 
  data.table(
    DESCR = c("RW", "PRJ", "MOD", "FIG", "DAT", "RES"),
    PATH  = c( RW ,  PRJ ,  MOD ,  FIG ,  DAT ,  RES )
  )

# Open Excel for storing results
if (file.exists(paste0(RES, "/", pXLSX, ".xlsx")) == TRUE) {
  invisible(file.remove(paste0(RES, "/", pXLSX, ".xlsx")))
}

if (pWSHT == TRUE) {
  fWriteToSheet(
    dtPATH, 
    RES, pXLSX, "PATHS", pAppend = FALSE )}

gvLOGO_PATH <- file.path(FIG, "GV_LOGO.png") 
if (!file.exists(gvLOGO_PATH)) {
  download.file(
    url      = "http://www.grandvision.com/img/logoGV.png",
    destfile = gvLOGO_PATH,
    mode     = 'wb')
}
knitr::include_graphics(gvLOGO_PATH)

# First execute the analysis zsANALYSIS-R1R2_MIG
# Extecute mcrAnalysesExtract
# C:\Users\fpadt\SAPEXPORT

read_and_union <- function(pTableName){
  
  dtReturn <- 
    do.call(
      rbind,
      lapply(as.list(SID.lng), function(x) {
        fGetEXPTable(
          pTableName = pTableName,
          pSystID = substr(x, 1, 3),
          pClient = substr(x, 4, 6) )
      }))
  
  return(dtReturn)
}

```

```{r logs, eval=FALSE, include=FALSE}

dtRSPCLOGCHAIN  <- read_and_union("RSPCLOGCHAIN")
dtRSPCLOGCHAIN[, DATUM := ymd(DATUM)]

dtRSPCCHAIN     <- read_and_union("RSPCCHAIN")
dtRSPCCHAINT    <- read_and_union("RSPCCHAINT")
dtRSPCCHAINATTR <- read_and_union("RSPCCHAINATTR")
dtRSPCTRIGGER   <- read_and_union("RSPCTRIGGER")

```

```{r Jobs, include=FALSE}
dtTBTCO     <- read_and_union("TBTCO")
dtTBTCP     <- read_and_union("TBTCP")
```


# Process Chains

This chapter focusses on the BI process chains and is structured in the 
following sections.

**Guide Lines:**  
First the general guidlines are given which apply to all process chains. 
In case a process chain deviates from these guide lines the reason must be 
documented. 

This paragraph contains an overview of all exisitng Process Chains per system.

**Configuration:**  
Next the configration of the Process Chains and alignment 
over the systems is discussed. 

**Loading:**  
Finally, the scheduling of the process chains is shown and discussed.
In general all process chains should be scheduled in all systems with the same 
frequency.  

Reasons to deviate from this need to be documented, e.g. 

- Local Chains are not scheduled in the project street  
- process chains in the project street might run at a higher frequency.  

This section will be split in several paragraphs regarding the status of the
Process chains:  

1. **live** and released in production (BP1).  
2. *not* **live** but are released in the Test/UAT system.  
3. *not* **live** and *not* released.  

\newpage

## General Guide Lines

Process Chains:  
1. are identical in all systems  
2. are scheduled at the same frequency in all systems  
3. have development class ZBI  

### Overview
The table below shows the number of process chains per system.  

This number can deviate in case new developments or deletions are not 
transported through the landscape. In case of deviations the open transport 
needs to be mentioned else the process chain will be flagged for deletion. 

Process Chains with development class **$TMP** will be deleted at the due date
given by the developer.  
Without a due data a $TMP process chain may be deleted instantaneously.


```{r transform_rspc_syst_01}
# determine Main Chains in all systems and count over all systems
dtRSPCMAIN <- 
  dtRSPCCHAIN[TYPE == "CHAIN", .(SYSTID, VARIANTE, TYPE)][
  dtRSPCCHAIN[TYPE == "TRIGGER", .(SYSTID, CHAIN_ID)],
    on = .(SYSTID, VARIANTE == CHAIN_ID)]                  %>%
  .[, MAIN := ifelse(is.na(TYPE), 1, 0)]                   %>%
  .[, `:=`(CHAIN_ID = VARIANTE,
           VARIANTE = NULL,
           TYPE     = NULL)]                               %>%
  unique()                                                 %>%
  .[, CNT := .N, by = .(CHAIN_ID)]                         %T>%
  setkey(CHAIN_ID)

dtRSPC_SYST <- 
  dtRSPCCHAINATTR[, TOT := .N, 
                  by = .(CHAIN_ID)]           %>%
  dcast.data.table(
    data          = ., 
    formula       = CHAIN_ID + TOT ~ SYSTID,
    fun.aggregate = length,  
    value.var     = "CHAIN_ID"
  )                                           %T>%
  setcolorder(c("CHAIN_ID", "TOT", SID.sht))  %T>%
  setorder(TOT, CHAIN_ID)

dtTMP01 <- 
  dcast.data.table(
    data = dtRSPCMAIN[, .N, 
                      by = .(SYSTID, MAIN)],
    formula = SYSTID ~ MAIN,
    fun.aggregate = sum,
    value.var = "N")                          %T>%
  setnames(c("0","1"), c("All","Main"))

if (pWSHT == TRUE) {
  fWriteToSheet(
    dtRSPC_SYST, 
    pPATH, pXLSX, "RSPC_SYST", pAppend = TRUE )}

```

```{r describe_RSPC_main_per_system, results='asis', }
kable(
  x = dtTMP01, 
  align = 'l',
  caption = "Number of Main Process Chains per System")

```

\newpage

## Configuration

This paragraph focusses on the configuration of the process chains

### Alignment
The following Process Chains are not in **ALL** systems! This list should be 
empty, currently it has `r nrow(dtRSPC_SYST[TOT < 5])` entries.  

The process chains do not have to be scheduled but the configuration 
needs to be aligned over all systems.

```{r describe_RSPC_alignment, results='asis'}
kable(
  x = dtRSPC_SYST[TOT < length(SID.lng)],
  align   = 'l',
  caption = "mis-alignment"
)
```

\newpage

## Loading & Errors

### Released in BP1

Process Chains which are released in production (BP1) need to be released in 
all other systems except Development, preferably at the same frequency.

### Released in TEST/UAT

Process Chains which are not released in production but are released in the 
Test/UAT systems are:  
1. New developents, being tested.  
2. Obsolete developments to be decommisioned.  
3. Temporary developents, to be documented  

### Scheduled

Process Chains which are not released in any system are either:  
1. Brand new  
2. Obsolete, to be deleted and transported to all systems  
3. Business Content, exist only in Development  

### Scheduling

The scheduling of the process chains can be determined from the historical logs
or from the settings in the starter variant of the Process Chain. 

The following historical Process Chain logs have been analyzed.

```{r describe_rspc, results='asis'}
kable(
  x = dtRSPCLOGCHAIN[
    , .(CHAINS = length(unique(CHAIN_ID)),
        FROM   = range(DATUM)[1],
        TO     = range(DATUM)[2],
        LOGS   = .N),
    by = .(ID = factor(SYSTID, levels = SID.sht, ordered = TRUE))] %>%
    setorder(ID))
```

\newpage

### Alignment

The table below shows the scheduling derived from the triggers

```{r transform_RSPC_trigger }
dtTRIG <- 
  dtRSPCCHAIN[
    TYPE == "TRIGGER", 
    .(SYSTID, CHAIN_ID, VARIANTE)][
      dtRSPCTRIGGER[
        , .(SYSTID   , VARIANTE,  STARTDTTYP,
            PRDMINS  , PRDHOURS, PRDDAYS  , PRDWEEKS, PRDMONTHS, 
            PERIODIC)
      ], 
      on = .(SYSTID, VARIANTE),
      nomatch = 0
      ] %>%
  .[, SYSTID := factor(
    x       = SYSTID, 
    levels  = c("BD1", "BA1", "BP1", "BTP", "BU1"), 
    ordered = TRUE) ]


if (pWSHT == TRUE) {
  fWriteToSheet(
    dtTRIG, 
    pPATH, pXLSX, "SCHED_TRIG", pAppend = TRUE )}
```

####  Scheduling by Minute

```{r describe_RSPC_trigger_prdmins, results='asis'}
kable(
  x = dcast.data.table(
    data = dtTRIG[
      PERIODIC   == "X" &
      STARTDTTYP == "D" &
      PRDMINS    != "0,00",
      .(SYSTID, CHAIN_ID,  PRDMINS)],
    formula = CHAIN_ID +  PRDMINS ~ SYSTID,
    fun.aggregate = length,
    value.var = "SYSTID"))
```

\newpage

#### Scheduling by Hour

```{r describe_RSPC_trigger_prdhours, results='asis'}
kable(
  x = dcast.data.table(
    data = dtTRIG[
      PERIODIC   == "X" &
      STARTDTTYP == "D" &
      PRDHOURS    != "0,00",
      .(SYSTID, CHAIN_ID,  PRDHOURS)],
    formula = CHAIN_ID + PRDHOURS ~ SYSTID,
    fun.aggregate = length,
    value.var = "SYSTID"))
```

\newpage

#### Scheduling by Day

```{r describe_RSPC_trigger_prddays, results='asis'}
kable(
  x = dcast.data.table(
    data = dtTRIG[
      PERIODIC   == "X" &
      STARTDTTYP == "D" &
      PRDDAYS    != "0,00",
      .(SYSTID, CHAIN_ID,  PRDDAYS)],
    formula = CHAIN_ID +  PRDDAYS ~ SYSTID,
    fun.aggregate = length,
    value.var = "SYSTID"))
```

\newpage

#### Logs

The table below shows the scheduling derived from the logs. 

```{r transform_RSPC_scheduling_logs_alignment}
dtRSPCLOGCHAIN[, DATUM:= ymd(DATUM)]

dtRSPC_SCHED <- 
  dcast.data.table(
    data          = dtRSPCLOGCHAIN[DATUM > ymd("20170501")], 
    formula       = CHAIN_ID ~ SYSTID,
    fun.aggregate = length,  
    value.var     = "CHAIN_ID"
  )                                         %>% 
  .[!(BA1 == BP1 | BA1 == BU1) ]            %T>%
  setcolorder(c("CHAIN_ID", SID.sht))

if (pWSHT == TRUE) {
  fWriteToSheet(
    dtRSPC_SCHED, 
    pPATH, pXLSX, "SCHED_LOG", pAppend = TRUE )}
```

```{r describe__RSPC_scheduling_logs_alignment, results='asis'}
kable(
  x = dtRSPC_SCHED,
  align = 'l',
  caption = "Scheduling from Logs")
```

### Scheduling based on last 7 days

```{r transform_RSPC_scheduling_logs_alignment_lw}

dtRSPC_SCHED_LW <- 
  dcast.data.table(
    data          = dtRSPCLOGCHAIN[DATUM > Sys.Date() - 7], 
    formula       = CHAIN_ID ~ SYSTID,
    fun.aggregate = length,  
    value.var     = "CHAIN_ID"
  )                                         %>% 
  .[!(BA1 == BP1 | BA1 == BU1) ]            %T>%
  setcolorder(c("CHAIN_ID", SID.sht))

if (pWSHT == TRUE) {
  fWriteToSheet(
    dtRSPC_SCHED_LW, 
    pPATH, pXLSX, "SCHED_LOG_LW", pAppend = TRUE )}
```

```{r describe__RSPC_scheduling_logs_alignment_lw, results='asis'}
kable(
  x = dtRSPC_SCHED_LW,
  align = 'l',
  caption = "Scheduling from Logs of last 7 days")
```

\newpage

### Loading Errors

This paragraph focusses on the loading errors in order to spot any problems and
determine actions for structural improvements. For this reason a log of Frequent
Failures and Fixes will be shown.

```{r transform_RSPC_loading_errors, echo=FALSE}

pBI <- "BP1"
acl <- c(A = "blue", G = "green", R = "red", X = "gray")

dtRSPC_GG <- 
  unique(dtRSPCLOGCHAIN[, .(SYSTID, CHAIN_ID, 
                            DATUM , ANALYZED_STATUS)])     %>%
  .[,            TEAM := substr(CHAIN_ID, 
                                start = 1, stop = 1)]      %>%
# .[TEAM == "0", TEAM := "G"]                              %>%
  dcast.data.table(
    data          = .,
    formula       = SYSTID + CHAIN_ID + DATUM + TEAM ~ ANALYZED_STATUS,
    fun.aggregate = length,
    value.var     = "TEAM"
  )                                                        %>%
  .[, STAT := ifelse(R == 0, "G", "R")]                    %>%
  .[DATUM > (Sys.Date() - 100), 
    `:=`(ORD = sum(R, na.rm = TRUE), N = .N), 
         by = .(SYSTID, CHAIN_ID, TEAM)]                   %>%
  .[dtRSPCMAIN, on = .(SYSTID, CHAIN_ID)]                  %>%
  .[, `:=`(
    FSYSTID = factor(
      x       = SYSTID, 
      levels  = c("BD1", "BTP", "BU1", "BA1", "BP1"), 
      ordered = TRUE),
    CH_ORD = 0L
    )]                                                     %>%
  .[SYSTID == "BP1", CH_ORD := ORD]
  
dtRSPC_EVOL <- 
  melt.data.table(
    data          = dtRSPC_GG[MAIN == 1     & 
                              TEAM == "G"],
    id.vars       = c("SYSTID", "DATUM"),
    measure.vars  = c("G", "R"),
    variable.name = "STATUS",
    na.rm         = TRUE
  )                                                        %>%
  .[, .(value = sum(value)), 
    by = .(SYSTID, DATUM, STATUS)]                         %>%
  rbind(., data.table(SYSTID = "BDP", DATUM = Sys.Date(), 
                      STATUS = "G"  , value = 0))          %>%
  .[, SYSTID_f := factor(
    x = SYSTID,
    levels  = c("BDP", "BTP", "BU1", "BD1", "BA1", "BP1"),
    ordered = TRUE)]

if (pWSHT == TRUE) {
fWriteToSheet(
  dcast.data.table(
    dtRSPC_GG[MAIN == 1     & 
                DATUM >= Sys.Date() - 100  ],
    formula       = CHAIN_ID ~ SYSTID,
    fun.aggregate = length,
    value.var     = "CHAIN_ID"), 
  pPATH, pXLSX, "CHAIN_UNI", 
  pAppend = TRUE )

write.table(
  dtRSPC_GG, 
  file      = "dtRSPC_GG.csv", 
  sep       = ";",
  row.names = FALSE, 
  col.names = TRUE)

write.table(
  dtRSPC_GG, 
  file      = "dtRSPC_EVOL.csv", 
  sep       = ";",
  row.names = FALSE, 
  col.names = TRUE)}

# rspc_main <- 
#   setdiff(dtRSPCCHAIN[SYSTID == pBI & TYPE == "TRIGGER", CHAIN_ID ],
#           dtRSPCCHAIN[SYSTID == pBI & TYPE == "CHAIN"  , VARIANTE])
# 
# dtRSPC_AMS1 <- 
#   unique(dtRSPCLOGCHAIN[, .(SYSTID, CHAIN_ID, DATUM, ANALYZED_STATUS)])
# 
# dtRSPC_AMS1 <- 
#   dtRSPC_AMS1[,  TEAM := substr(CHAIN_ID, start = 1, stop = 1)][
#     TEAM == "0", TEAM := "G"]

# dtRSPC_AMS2 <- 
#    dtRSPC_AMS1[, .(CNT = .N), 
#                by = .(SYSTID, CHAIN_ID, TEAM, ANALYZED_STATUS)]

# dtRSPC_AMS3 <-
#   dcast.data.table(
#   data          = dtRSPC_AMS1[SYSTID == pBI & CHAIN_ID %in% rspc_main],
#   formula       = CHAIN_ID + DATUM + TEAM ~ ANALYZED_STATUS,
#   fun.aggregate = length,
#   value.var     = "TEAM"
#   ) 

# dtRSPC_AMS3[, STAT := ifelse(R == 0, "G", "R")]
# setkey(dtRSPC_AMS3, CHAIN_ID, DATUM)
# 
# dtRSPC_AMS4 <- 
#   dtRSPC_AMS3[DATUM > ymd("20161231")][, ORD := 0L]
# dtRSPC_AMS4[DATUM > (Sys.Date() - 100), 
#             ORD := sum(R), by = .(CHAIN_ID, TEAM)]


# dtRSPC_SUM <- 
#   dcast.data.table(
#     data          = dtRSPCLOGCHAIN, 
#     formula       = SYSTID + CHAIN_ID + DATUM ~ ANALYZED_STATUS,
#     fun.aggregate = length 
#   )
# 
# dtRSPC_SUM[, V1:= NULL]
# 
# dtRSPC_DAY <- copy(dtRSPC_SUM)
# dtRSPC_DAY[, `:=` (AD = A > 0,
#                    GD = G > 0,
#                    RD = R > 0,
#                    XD = X > 0)]

# dtRSPC_TDY <- 
#   dtRSPC_DAY[, .(A  = sum(A),
#                  G  = sum(G),
#                  R  = sum(R),
#                  X  = sum(X),
#                  AD = sum(AD),
#                  GD = sum(GD),
#                  RD = sum(RD),
#                  XD = sum(XD)), 
#              by = .(SYSTID, DATUM)]
# 
# dtRSPC_TDY[, DATUM:= ymd(DATUM)]

# ggplot(data = dtRSPC_TDY, mapping = aes(x = DATUM, y = RD)) +
#   geom_line() +
#   facet_wrap(facets = "SYSTID", nrow = 3)
# 
# ggplot(data = dtRSPC_DAY, 
#        mapping = aes(x = DATUM, y = RD, color = as.factor(CHAIN_ID),
#                      group = as.factor(CHAIN_ID))) +
#   geom_line() +
#   facet_wrap(facets = "SYSTID")

# ggplot(data    = dtRSPCLOGCHAIN[DATUM > ymd("20160801") & 
#                                   ANALYZED_STATUS == "R"],
#        mapping = aes(x = CHAIN_ID, fill = ANALYZED_STATUS )) + 
#   geom_bar() +
#   coord_flip()


# ggP2 <-
#   ggplot(data = dtRSPC_AMS2[SYSTID == pBI &
#                             CHAIN_ID %in% rspc_main]) +
#   geom_col(mapping  = aes(x    = CHAIN_ID, 
#                           y    = CNT,  
#                           fill = ANALYZED_STATUS),
#            position = "stack") +
#   coord_flip() +
#   scale_fill_manual(values = acl) +
#   facet_wrap(
#     facets = "TEAM"
#     )
# ggP2

# ggP3 <- 
#   ggplot(data = dtRSPC_AMS3, 
#          aes(x = DATUM, 
#              y = CHAIN_ID)) +
#   geom_raster(aes(fill = STAT)) +
#   scale_fill_manual(values = colours ) +
#   theme(legend.position = "top")
# ggP3
# 
# ggP4 <- 
#   ggplot(data = dtRSPC_AMS4[ORD > 0], 
#          aes(x = DATUM, 
#              y = reorder(CHAIN_ID, 
#                          ORD, 
#                          function(x){sum(x)} ))) +
#   geom_raster(aes(fill = STAT)) +
#   scale_fill_manual(values = acl ) +
#   theme(legend.position = "top") +
#   labs(title = pBI,
#     x = "Day",
#     y = "Proc Chain") +
#   facet_wrap(
#     facets = "TEAM"
#     )
# ggP4
```


```{r visualize_RSPC_loading_errors, fig.height=15, fig.width=20, results='asis'}
#Visualize the loading errors per syste/Chain
# setdiff(unique(dtRSPC_GG$TEAM), NA)
for (pTEAM in c("0", "G", "L"))  {
  
  cat("\n\n\\newpage\n")
#  writeLines("ValueForV")
    
  ggP5 <- 
    ggplot(data = dtRSPC_GG[MAIN == 1     & 
                            TEAM == pTEAM &
                            DATUM >= Sys.Date() - 100  ], 
           aes(x = DATUM, 
               y = reorder(CHAIN_ID, 
                           CH_ORD, 
                           function(x){sum(x, na.rm = TRUE)} ))) +
    geom_raster(aes(fill = STAT)) +
    scale_fill_manual(values = acl ) +
    theme(legend.position = "top") +
    labs(
      x = "Day",
      y = "Proc Chain") +
    facet_grid(
      facets = TEAM ~ FSYSTID
    )
  print(ggP5)
  
  ggsave(
    filename = paste0("./70_figures/", pTEAM, "_RSPC.jpg"),
    plot     = ggP5,
    device   = "jpeg",
    width    = 30, 
    height   = 20, 
    units    = "cm"   
  )
}

cat("\n\n\\pagebreak\n")
# writeLines("ValueForV")
    
# Visualize the Evolution of Errors
ggEVOL <- 
  ggplot(data = dtRSPC_EVOL) +
  geom_bar(mapping = aes(x      = DATUM, 
                          y     = value,
                          color = STATUS,
                          fill  = STATUS),
            size = 1,
           position = "stack",
           stat     = "identity") +
  scale_color_manual(values = c(G = "green3", R = "red2") )         +
  scale_fill_manual(values  = c(G = "green3", R = "red2") )          +
  theme(legend.position = "top") +
  labs(
    x = "Day",
    y = "# Main Chain's per day") +
  facet_wrap(
    facets = "SYSTID_f"
  )
ggEVOL

ggsave(
    filename = paste0("./70_figures/", "RSPC_EVOL.jpg"),
    plot     = ggEVOL,
    device   = "jpeg",
    width    = 30, 
    height   = 20, 
    units    = "cm"   
  )

```


```{r Check_Existence, eval=FALSE, include=FALSE}
dtRSPCCHAINATTR[, CNT := .N, by = .(CHAIN_ID)]
if (pWSHT == TRUE) {
  fWriteToSheet(dtRSPCCHAINATTR[CNT < 5 ], 
                pPATH, pXLSX, "Non_existing_chains", pAppend = TRUE )}
```


```{r Scheduling_per_System}
dtTBCT <- 
  dtTBTCO[JOBNAME        == "BI_PROCESS_TRIGGER" &
          PERIODIC       == "X"                  &
          STATUS         == "S"                  &
          EVENTID        == "" ]                            %>%
  dtTBTCP[., on = .(SYSTID, JOBNAME, JOBCOUNT, STEPCOUNT)]  %>%
  .[, AUTHCKMAN := ifelse(SYSTID == "BD1", "100", "300")]   

write.table(dtTBCT, 
            file = "C:/Users/fpadt/OneDrive - GrandVision/Documents/RSPC_VAR.txt", 
            sep = ";", row.names = FALSE, col.names = TRUE)

# read.table(file = "C:\Users\fpadt\OneDrive - GrandVision\Documents\tblRSPC_CHAIN.txt", sep="")
```

