---
title   : "Quality Assurance Report"
subtitle: "Users & Authorization"
author  : "F.J. Padt"
date    : "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    toc: yes
  pdf_document:
    highlight: tango
    toc: yes
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

```{r setup}

# Cleanse memory
rm(list = ls())
gc()

# Data Settings
pXLSX    <- "Authorization" 
pWSHT    <- TRUE
newfiles <- TRUE

# KnitR SetUp location
KS   <- file.path("~", "RW",
                  "QAR", "00_RProj", "00_Global", "KnitR_SetUp.R")

# Load functions
invisible(source(KS))

# Constants
# folder  <- "/bi/ib/md"          
# lfolder <- file.path("..", folder)  # local folder
# fsurl   <- paste0(
#   "ftp://fs.grandvision.com/pythia/", folder)
# userpwd <- paste("ftpbp1", params$password, sep = ":")

```

[R4DS](http://r4ds.had.co.nz/introduction.html)

# Read Tables
```{r Import}

T1 <- Sys.time()

dtUSGRP <- 
  fRead_and_Union(
    pType    = "B", 
    pTable   = "USGRP",
    pOptions = list())

dtUSGRPT <- 
  fRead_and_Union(
    pType    = "B", 
    pTable   = "USGRPT", 
    pOptions = list("SPRSL = 'E'"))

dtUSGRP_USER <-
  fRead_and_Union(
    pType    = "B", 
    pTable   = "USGRP_USER", 
    pOptions = list())

dtUSR02 <- 
  fRead_and_Union(
    pType    = "B", 
    pTable   = "USR02", 
    pOptions = list(),
    pFields  = list(
      'MANDT'   , 'ANAME'     , 'BNAME', 'ERDAT', 
      'TRDAT'   , 'LTIME'     , 'GLTGV', 'GLTGB', 
      'USTYP'   , 'CLASS'     , 'LOCNT', 'UFLAG',
      'PWDSTATE', 'PWDINITIAL', 'PWDLOCKDATE'))

dtAGR_USERS <- 
  fRead_and_Union(
    pType    = "B", 
    pTable   = "AGR_USERS", 
    pOptions = list())

dtUSR21 <- 
  fRead_and_Union(
    pType    = "B", 
    pTable   = "USR21", 
    pOptions = list())

dtADR6 <- 
  fRead_and_Union(
    pType    = "B", 
    pTable   = "ADR6", 
    pOptions = list())

# AGR_DEFINE

# 
dtAUTH       <-
  fRead_and_Union(
    pSIDCLNT = c("BU1300", "BA1300", "BP1300"),
    pTable   = "/BIC/AG1AAPD222",
    pOptions = list(),
    pFields  = list(
      '/BIC/G1AAGRP', 
      '/BIC/G1AAOBJ',
      '/BIC/G1AAOPT', 
      '/BIC/G1AASIGN',
      '/BIC/G1AAVAL_H',
      '/BIC/G1AAVAL_L', 
      '/BIC/G1COUNT',
      'RECORDMODE'
    ))

dtRES <- dtUSR02[dtAGR_USERS, on = .(SYSTID, BNAME = UNAME )]

write.table(
  dtRES, file = "c:/c-temp/RES.csv",
  sep = ";", row.names = FALSE, col.names = TRUE)

dtRES <- dtUSR02[dtAGR_USERS, on = .(SYSTID, BNAME = UNAME )]
write.table(
  dtRES, file = "c:/c-temp/RES.csv",
  sep = ";", row.names = FALSE, col.names = TRUE)
```

```{r Tidy}



```

```{r Visualize}

```


```{r Model}

```


```{r Communicate}

dtUSER_PVT <- 
  dcast.data.table(
    data = dtUSR02,
    formula = BNAME 
    + USTYP + CLASS + TRDAT + GLTGB  + UFLAG
    ~ SYSTID,
    fun.aggregate = length,
    value.var = "SYSTID")                    %>%  
  .[, Total := BS1 + BD1 + BU1 + BA1 + BP1]        %T>%
  setcolorder(
    c("BNAME", "USTYP", "CLASS", "TRDAT", "GLTGB", "UFLAG",
      "BS1", "BD1", "BU1", "BA1", "BP1", "Total"))

pFFN <- file.path("~", "RW", "QAR", "30_Analysis", "dtUSER_PVT.csv")

write.table(
  dtUSER_PVT,
  file = pFFN, sep = ";", row.names = FALSE)
shell.exec(normalizePath(pFFN))

dtRES <- dtUSR02[dtAGR_USERS, on = .(SYSTID, BNAME = UNAME )]

pFFN <- file.path("~", "RW", "QAR", "30_Analysis", "RES.csv")

write.table(
  dtRES,
  file = pFFN, sep = ";", row.names = FALSE)
shell.exec(normalizePath(pFFN))

```


  # read data from MS Access extract


  
# load("./11_PrepData/dtDUMMIES.RData")
# load("~/RW/QAR/11_PrepData/dtDUMMIES.RData")
# load("~/RW/QAR/11_PrepData/dtEMAIL.RData")
# load("~/RW/QAR/11_PrepData/dtSAPDUMMY.RData")  
  
  # dtAUTH       <- fGetEXPTable(pTableName = "#BIC#AG1AAPD0200"
  #                              , pSystID = "BP1", pClient = 300)  
  
  # Read data from Local Excel File, note stats need to be refreshed
  # dtCOMM       <- as.data.table(read_excel(path = pINFO, sheet = "C.OMMENT"))
  
 } 

```

```{r}
dtUSR <- 
  dtUSR02[USTYP == "A", 
          .(SYSTID, MANDT, BNAME, GLTGB, CLASS, UFLAG,
            TRDAT, PWDSTATE, PWDINITIAL, PWDLOCKDATE )]        %T>%
  setnames(c("GLTGB"), c("USR_GLTGB"))

dtUSR_GRP <- 
  dtUSGRP_USER[, .(SYSTID, MANDT, BNAME, USERGROUP)]

dtUSR_AGR <- 
  dtAGR_USERS[, .(SYSTID, MANDT, AGR_NAME, UNAME, TO_DAT)]     %T>%
  setnames(c("TO_DAT"), c("AGR_TO_DAT"))

dtAUTH <- 
  dtUSR_AGR[dtUSR, on = .(SYSTID, MANDT, UNAME = BNAME)]      %>%
  dtUSR_GRP[., on = .(SYSTID, MANDT, BNAME = UNAME), allow.cartesian = TRUE]

pFFN <- normalizePath(file.path("~", "RW", "QAR", "30_Analysis", "auths.csv"))

write.table(
  dtAUTH,
  file = pFFN, sep = ";", row.names = FALSE)
shell.exec(pFFN)


```

