---
title   : "Quality Assurance Report"
subtitle: "Inactive Objects"
author  : "F.J. Padt"
date    : "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_notebook:
    toc: yes
  pdf_document:
    highlight: tango
    toc: yes
    toc_depth: 4
editor_options: 
  chunk_output_type: inline
---

```{r setup}

# # Cleanse memory
# rm(list = ls())
# gc()

# parameters Settings
pXLSX    <- "InActive-Objects" 
pWSHT    <- TRUE
newfiles <- TRUE

# KnitR SetUp location
KS   <- file.path("..", "00_Global", "KnitR_SetUp.R")

# Load functions
invisible(source(KS))

lstVERS <- list("OBJVERS <> 'D'") #"OBJSTAT = 'INA'", "AND", 
lstLANG <- list("LANGU = 'EN'") #"OBJSTAT = 'INA'", "AND", 

```

    g_t_cube,
    g_t_iobj,
    g_t_updr,
    g_t_ods,
    g_t_ohd,
    g_t_dtp,
    g_t_stru,
    g_t_apd,
    g_t_copr,
    g_t_tadir,
    
```{r add_new_read_ZTBW_INA_SNAP}
load(file = file.path("..", "..", "11_PrepData", "dtZTBW_INA_SNAP.RData"))

dtZTBW_INA_SNAP_N <- 
  fReadSAPTable(
    pSystID  = "BP1",
    pClient  = "300", 
    pTable   = "ZTBW_INA_SNAP",
    pOptions = list(),
    pFields  = fGetFields(pSYSTID = "BP1", pCLIENT = "300", pTable = "ZTBW_INA_SNAP"))

dtZTBW_INA_SNAP <- 
  rbindlist(list(dtZTBW_INA_SNAP, dtZTBW_INA_SNAP_N)) %>%
  unique(.)

save(dtZTBW_INA_SNAP, file = file.path("..", "..", "11_PrepData", "dtZTBW_INA_SNAP.RData"))

pXLSX <- "ZTBW_INA_SNAP"
if (pWSHT == TRUE) {
  fWriteToSheet(
    dtZTBW_INA_SNAP, 
    RES, pXLSX, "SNAPSHOT", pAppend = FALSE )}
shell.exec(file.path(RES, paste0(pXLSX, ".xlsx")))
```

## Cubes
    
```{r}


dtRSDCUBE <- 
  fReadSAPTable(
    pSystID  = "BA1",
    pClient  = "300", 
    pTable   = "RSDCUBE",
    pOptions = lstVERS,
    pFields  = list("INFOCUBE", "OBJVERS", "OBJSTAT",
                    "CUBETYPE", "TSTPNM" , "TIMESTMP")) %>%
  fReadSAPTable(
    pSystID  = "BA1",
    pClient  = "300", 
    pTable   = "RSDCUBET",
    pOptions = lstLANG,
    pFields  = list("INFOCUBE", "OBJVERS", "TXTLG"))[
      ., on = .(SYSTID, CLIENT, INFOCUBE, OBJVERS), nomatch = NA]


```
    
## InfoObjects

```{r}

dtRSDIOBJ <- 
  fReadSAPTable(
    pSystID  = "BA1",
    pClient  = "300", 
    pTable   = "RSDIOBJ",
    pOptions = lstVERS,
    pFields  = list("IOBJNM", "OBJVERS", "OBJSTAT", 
                    "IOBJTP", "TSTPNM", "TIMESTMP")) %>%
  fReadSAPTable(
    pSystID  = "BA1",
    pClient  = "300", 
    pTable   = "RSDIOBJT",
    pOptions = lstLANG,
    pFields  = list("IOBJNM", "OBJVERS", "TXTLG"))[
      ., on = .(SYSTID, CLIENT, IOBJNM, OBJVERS), nomatch = NA]



```

## Transformations

    SELECT tranid tranid AS obj_name sourcename
           orgtranid AS org_obj_name           " +<DBORGIE_03062015>
           targetname tstpnm timestmp
       FROM rstran

```{r}

dtRSTRAN <- 
  fReadSAPTable(
    pSystID  = "BA1",
    pClient  = "300", 
    pTable   = "RSTRAN",
    pOptions = lstVERS,
    pFields  = list("TRANID"   , "OBJVERS"   , "OBJSTAT", "SOURCENAME",
                    "ORGTRANID", "TARGETNAME", "TSTPNM" , "TIMESTMP")) 



```

## Update Rules

Used in Technical Content
     
```{r}

dtRSUPDINFO <- 
  fReadSAPTable(
    pSystID  = "BA1",
    pClient  = "300", 
    pTable   = "RSUPDINFO",
    pOptions = lstVERS,
    pFields  = list("UPDID"  , "OBJVERS" , "OBJSTAT", 
                    "ISOURCE", "INFOCUBE", "TSTPNM" , "TIMESTMP"))  

```

## ODSO

    SELECT o~odsobject o~odsobject AS obj_name o~odsotype
           o~tstpnm o~timestmp t~txtlg
     INTO CORRESPONDING FIELDS OF TABLE g_t_ods
      FROM rsdodso
      
     
```{r}

dtRSDODSO <- 
  fReadSAPTable(
    pSystID  = "BA1",
    pClient  = "300", 
    pTable   = "RSDODSO",
    pOptions = lstVERS,
    pFields  = list("ODSOBJECT", "OBJVERS",  
                    "ODSOTYPE" , "TSTPNM" , "TIMESTMP")) %>%
  fReadSAPTable(
    pSystID  = "BA1",
    pClient  = "300", 
    pTable   = "RSDODSOLOC",
    pOptions = list(),
    pFields  = list("ODSOBJECT", "OBJSTAT", "ACTIVFL"))[
      ., on = .(SYSTID, CLIENT, ODSOBJECT), nomatch = 0] %>%
  fReadSAPTable(
    pSystID  = "BA1",
    pClient  = "300", 
    pTable   = "RSDODSOT",
    pOptions = lstLANG,
    pFields  = list("ODSOBJECT", "OBJVERS", "TXTLG"))[
      ., on = .(SYSTID, CLIENT, ODSOBJECT, OBJVERS), nomatch = NA]



```

## ADSO

The following list shows all ADSO's in the system. 
The inactive ADSO's are shown at the top (if any) and ADSO are sorted alphabetical within
their OBJSTAT
      
```{r}
 
dtRSOADSO <-
  fGetLIST_ADSO(pSystID = "BP1", "300") %>%
  fReadSAPTable(
    pSystID  = "BP1",
    pClient  = "300", 
    pTable   = "RSOADSOLOC",
    pOptions = list(),
    pFields  = list("ADSONM", "OBJSTAT", "ACTIVFL"))[
      ., on = .(SYSTID, CLIENT, ADSONM = OBJNM), nomatch = 0] %T>%
  setorder(-OBJSTAT, ADSONM)

knitr::kable(dtRSOADSO[
  OBJSTAT == "ACT", .(ADSONM, OBJSTAT, ACTIVFL, TXTLG)])
```

## Open Hub

    SELECT o~ohdest o~ohdest AS obj_name o~desttype
           o~tstpnm o~timestmp t~txtlg
     INTO CORRESPONDING FIELDS OF TABLE g_t_ohd
      FROM rsbohdest AS o
      LEFT OUTER JOIN rsbohdestt AS t
      ON  t~ohdest  = o~ohdest
      AND t~objvers = o~objvers
      AND t~langu   = sy-langu
      
```{r}
RSB_API_OHS_DEST_GETLIST
```

      
## DTPs

    SELECT a~dtp a~dtp AS obj_name b~src b~tgt
           b~dtptype b~tstpnm b~timestmp b~dtp_original AS org_obj_name
     INTO CORRESPONDING FIELDS OF TABLE g_t_dtp
     FROM rsbkdtpstat AS a

     INNER JOIN rsbkdtp AS b
      ON a~dtp = b~dtp
    WHERE a~objstat = gc_objstat_ina.
    
## Transfer Structures

    SELECT transtru transtru AS obj_name logsys tstpnm timestmp
      FROM rsts
      
## ADP

    SELECT a~process a~process AS obj_name a~tstpnm a~timestmp t~txtlg
      FROM rsant_process AS a
      LEFT OUTER JOIN rsant_processt AS t

## COPR

    SELECT copr~objnm       AS objnm
           copr~objnm       AS obj_name
           copr~changedby   AS tstpnm
           copr~changedat   AS timestmp
           t~description    AS txtlg
           copr~objvers

       FROM rsltip AS copr

       LEFT OUTER JOIN rsltipt AS t

## HCPR

    SELECT hcpr~hcprnm      AS objnm
           hcpr~hcprnm      AS obj_name
           hcpr~tstpnm
           hcpr~timestmp
           t~description    AS txtlg
           hcpr~objvers

       FROM rsohcpr AS hcpr

     LEFT OUTER JOIN rsohcprt AS t
     
```{r}
# Error
dtRSOHCPR <- 
  # fReadSAPTable(
  #   pSystID  = "BA1",
  #   pClient  = "300", 
  #   pTable   = "RSOHCPR",
  #   pOptions = lstVERS,
  #   pFields  = list("HCPRNM", "OBJVERS",  
  #                   "TSTPNM", "TIMESTMP")) %>%
  fReadSAPTable(
    pSystID  = "BA1",
    pClient  = "300", 
    pTable   = "RVPHCPR",
    pOptions = lstLANG,
    pFields  = list("HCPRNAME"))
# [
#       ., on = .(SYSTID, CLIENT, HCPRNM, OBJVERS), nomatch = NA]



```
      
      
## Queries

RSCRM_IMP_EXEC_QUERY_READ_DATA